Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-25 paper.qmd
Updated 7c

mse_two_curvy_b <- ggplot(error_two_curvy_tsne, 
                     aes(x = a1, 
                         y = RMSE)) +
  geom_vline(xintercept = 0.03,
           colour = "#d95f02", linetype="dashed", 
           linewidth=1) +
  geom_vline(xintercept = 0.05,
             colour = "#1f78b4", 
             linetype="solid",
             linewidth=1) +
  geom_vline(xintercept = 0.08, linetype="dotted",
             colour = "#1b9e77", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_tsne$a1, 2)))[c(1, 4, 7, 11, 13, 14, 15, 16)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "RMSE") +
  interior_annotation("a", position = c(0.9, 0.1), cex = 2) +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 20, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

@@

mse_two_curvy_lwd <- ggplot(error_rm_two_curvy, 
                     aes(x = benchmark_rm_lwd, 
                         y = RMSE,
                         colour = a1,
                         linetype = a1)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.5
    ) + 
  scale_x_continuous(breaks = sort(unique(error_rm_two_curvy$benchmark_rm_lwd))[c(1, 3, 5, 7, 9, 11, 13, 15, 17)]) +
  scale_color_manual(values=c("#d95f02", "#1f78b4", "#1b9e77"),
                     labels = parse_format()) +
  scale_linetype_manual(values = c("dashed", "solid", "dotted"),
                        labels = parse_format()) +
  xlab("bin density cutoff") +
  ylab("RMSE") +
  interior_annotation("c", position = c(0.07, 0.9), cex = 2) +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 20, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        axis.title = element_text(size = 18),
axis.text = element_text(size = 15))
```

@@

mse_two_curvy_b + a1_m_two_curvy +
  mse_two_curvy_lwd + prop_dens_a1 +
  plot_layout(ncol=2)
```

>>>>

rmse_two_curvy_b <- ggplot(error_two_curvy_tsne, 
                     aes(x = a1, 
                         y = RMSE)) +
  geom_vline(xintercept = 0.03,
           colour = "#d95f02", linetype="dashed", 
           linewidth=1) +
  geom_vline(xintercept = 0.05,
             colour = "#1f78b4", 
             linetype="solid",
             linewidth=1) +
  geom_vline(xintercept = 0.08, linetype="dotted",
             colour = "#1b9e77", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_tsne$a1, 2)))[c(1, 4, 7, 11, 13, 14, 15, 16)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "RMSE") +
  interior_annotation("a", position = c(0.9, 0.1), cex = 2) +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 20, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

@@

rmse_two_curvy_lwd <- ggplot(error_rm_two_curvy, 
                     aes(x = benchmark_rm_lwd, 
                         y = RMSE,
                         colour = a1,
                         linetype = a1)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.5
    ) + 
  scale_x_continuous(breaks = sort(unique(error_rm_two_curvy$benchmark_rm_lwd))[c(1, 4, 7, 11, 17, 21)]) +
  scale_color_manual(values=c("#d95f02", "#1f78b4", "#1b9e77"),
                     labels = parse_format()) +
  scale_linetype_manual(values = c("dashed", "solid", "dotted"),
                        labels = parse_format()) +
  xlab("bin density cutoff") +
  ylab("RMSE") +
  interior_annotation("c", position = c(0.07, 0.9), cex = 2) +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 20, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        axis.title = element_text(size = 18),
axis.text = element_text(size = 15))
```

@@

rmse_two_curvy_b + a1_m_two_curvy +
  rmse_two_curvy_lwd + prop_dens_a1 +
  plot_layout(ncol=2)
```
